Improving Multi-Domain Neural Machine Translation with Differential Data Selection

### 2021-01-31 2021/acl-ijcnlp2021/mdmt.tex
write section 2, section 3

\section{Introduction}\label{sec:intro}
A typical setting in machine translation, is to collect the largest possible collection of parallel data for the chosen language pair, with the intent to achieve optimal performance for a task of interest. In such situations, the training data distribution is opportunistic, while the test data distribution is chosen; a key component in training is then to mitigate the detrimental effects of this mismatch between distributions. Single-source and multi-source domain adaptation is a well-studied instance of this setting (see \cite{Chu2017comparison} for a review) , and so is multi-domain learning \cite{Chu18multilingual,Zeng18multidomain,Jiang19multidomain}. A related situation is multi-lingual machine translation \cite{Firat16multiway,Ha16towards,Johnson17google}\fyTodo{Add more recent work}, where the heterogeneity of training data correspond not only to variation in topic or genre, but also in languages.

\fyTodo{Label or covariate shift ?}
This problem is often approached with instance selection or reweighting strategies, where the available training data is used in proportion to its relevance for the test conditions. [Additional techniques : GANs for feau]

>>>>

\section{Introduction}\label{sec:intro}
A typical setting in machine translation, is to collect the largest possible collection of parallel data for the chosen language pair, with the intent to achieve optimal performance for a task of interest. In such situations, the training data distribution is opportunistic, while the test data distribution is chosen; a key component in training is then to mitigate the detrimental effects of this mismatch between distributions. Single-source and multi-source domain adaptation is a well-studied instance of this setting (see \cite{Chu2017comparison} for a review) , and so is multi-domain learning \cite{Chu18multilingual,Zeng18multidomain,Jiang19multidomain}. A related situation is multi-lingual machine translation \cite{Firat16multiway,Ha16towards,Johnson17google,Arivazhagan19massively}\fyTodo{Add more recent work}, where the heterogeneity of training data not only corresponds to variation in topic or genre, but also in language.

\fyTodo{Label or covariate shift ?}
This problem is often approached with instance selection or reweighting strategies, where the available training data is used in proportion to its relevance for the chosen test conditions. Finding the optimal balance of training data is however a challenging task due for instance to similarity between domains / languages. Several recent proposals \cite{Kumar19reinforcement}
